Survivable Set Connectivity

### 2015-05-08 draft.tex
started correctness proof

In order to understand the ideas of the algorithm, it is important to understand the ideas of the analysis. We summarize the ideas of the analysis here:
\begin{enumerate}
\item Set a particular set of edges $F$ of size at most $\Omega(\dfrac{k}{\log n})$. 
\item Argue that with probability at most $\frac{1}{2}$, the edges in $F$ are not necessary for connectivity by claiming that the total $load$ on the edges in low. 
\item We will condition on this probability to show that if we remove $\text{map}(F)$ on the tree, we still have sufficient flow from each $s_i$ to $t_i$. This flow must go up the tree to some common ancestor $v$ and then back down.
\item Then we will claim that at some $v$, it gets marked and the RoundGKR algorithm which is rooted at $v$ finds the two paths from $v$ to $s_i$ and $t_i$, and so the path will be included with sufficient probability and exclude $F$.
\item We finally union bound over all $F$ and over all $i$ to show that we succeed with constant probability. 
\end{enumerate}

@@

>>>>

@@

Having established that the expected cost is only polylogarithmic away from the optimum, it remains to show that the edges chosen do in fact form a graph which connects $(S_i, T_i)$ with $\Omega(\frac{k}{\log n})$ disjoint paths for each $i$.

\begin{definition}
For some set of edges $F \subset E$, the sampled tree embedding, $(T, y, \text{map})$ is bad if $F_T = \text{map}^{-1}(F)$ 
\[ \sum_{e' \in F_T} y_{e'} \geq \frac{1}{2} \]
And good otherwise.
\end{definition}

Intuitively, bad sets correspond to sets which are necessary in the graph. We want graphs to be good with respect to sets of size $\Omega(\frac{k}{\log n})$ in order to ensure connectivity.

\begin{lemma}
\label{lem:notbad}
Fix some $F$, or size at most $\dfrac{k}{16 \alpha}$. Then the probability that a sampled tree embedding $(T, y, \text{map})$ from $\mathcal{D}$ is bad is at most $\frac{1}{2}$. 
\end{lemma}

\begin{proof}
Suppose we have a bad embedding for the set $F$. Then 
\begin{align}
\sum_{e \in F} load(e)&= \sum_{e \in F} \sum_{e' \in \text{map}^{-1}(e)} y_{e'} \\
                    &\geq \sum_{e' \in F_T} y_{e'} \\
                    &\geq \frac{1}{2}
\end{align}
Where the first inequality we get from taking the sum over the union versus the disjoint union, and the second inequality from the assumption that the tree embedding is bad.

Therefore, a bad tree means that the load of the set of $F$ is more than $\frac{1}{2}$. Therefore,
\begin{align}
Pr[\text{pick a bad tree for $F$}] &\leq Pr[ \sum_{e\in F} load(e) \geq \frac{1}{2}]
\end{align}
From Lemma~\ref{lem:rload}, we know that
\begin{align}
\textbf{E}[ \sum_{e \in F} load(e) ] &\leq \sum_{e \in F} \textbf{E}[rload(e)]x_{e'} \\
                                   & \leq \sum_{e\in F} \alpha \frac{4}{k} x_{e} \\
                                   & \leq \dfrac{4\alpha}{k} |F| \\
                                   &\leq \frac{1}{4}
\end{align}
Since we limited the size of $F$. Now invoking Markov's inequality, we know that the probability of bad event is at most $\frac{1}{2}$. 
\end{proof}

\begin{lemma}
With probability at least $\frac{3}{4}$, all set pairs are at least $\frac{k}{16\alpha} + 1$ edge connected in $H$. 
\end{lemma}

\textbf{Proof Idea}:
\begin{enumerate}
\item Set a particular set of edges $F$ of size at most $\Omega(\dfrac{k}{\log n})$. 
\item Argue that with probability at most $\frac{1}{2}$, the edges in $F$ are not necessary for connectivity by claiming that the total $load$ on the edges in low. (This is Lemma~\ref{lem:notbad}). 
\item We will condition on this probability to show that if we remove $\text{map}(F)$ on the tree, we still have sufficient flow from each $s_i$ to $t_i$. This flow must go up the tree to some common ancestor $v$ and then back down.
\item Then we will claim that at some $v$, it gets marked and the RoundGKR algorithm which is rooted at $v$ finds the two paths from $v$ to $s_i$ and $t_i$, and so the path will be included with sufficient probability and exclude $F$.
\item We finally union bound over all $F$ and over all $i$ to show that we succeed with constant probability. 
\end{enumerate}

\begin{proof}
We fix an $F$ of size at most $\frac{k}{16\alpha}$ and an $i$ and show that $(S_i, T_i)$ are connected with an edge outside of $F$. I will show this happens with a probability at least $\beta$. So the probability of failure is $(1-\beta)$. If we repeat this $\tau = \frac{1}{\beta}\ln(4hn^{\frac{k}{16\alpha}})$ times, then our failure probability goes down to $\dfrac{1}{4hn^{\frac{k}{16\alpha}}}$. So now we take the union bound over all of $F$ and over all $i$, so we get probability of failure at most $\frac{1}{4}$.   
\end{proof}
